\begin{enumerate}
\item Елфимов Сергей
Викторович. Многоканальная теория квантового дефекта для полярных молекул: диссертация ... кандидата физико-математических
наук: 01.04.05 / Елфимов
Сергей
Викторович;[Место
защиты: Воронежский государственный
университет].-
Воронеж, 2014.- 95 с.
\item
\href{http://xn--90ax2c.xn--p1ai/search/?f_field%5bauthorbook%5d=f/authorbook/%D0%B0%D0%BB%D1%87%D0%B5%D0%B5%D0%B2+%D0%BF.%D0%B3.}{Алчеев П.Г.} Силы осцилляторов электронных переходов между ридберговскими состояниями эксимерных молекул NeH и ArH : автореф. дис. ... канд. физ.-мат. наук : 01.04.05 / П.Г. Алчеев
\item \foreignlanguage{english}{Bell M. B., Avery L. W., Seaquist E. R., Vallee J. P. A New Technique for}
\end{enumerate}
\foreignlanguage{english}{Measuring Impact broadened Radio Recombination Lines in Hii Regions: Confrontation with Theory
at High Principal Quantum Numbers // Publications of the Astronomical Society of the Pacific. 2000. Vol. 112. P.
1236--1242.}

\liststyleWWNumi
\setcounter{saveenum}{\value{enumi}}
\begin{enumerate}
\setcounter{enumi}{\value{saveenum}}
\item \foreignlanguage{english}{Yoshida S., Reinhold C. O., Burgd\"orfer J. et al. Photoexcitation of }\newline
$n$\foreignlanguage{english}{
}\foreignlanguage{english}{\textit{${\simeq}$}}\foreignlanguage{english}{
}\foreignlanguage{english}{\textit{305}}\foreignlanguage{english}{ Rydberg states in the presence of an rf drive field
// Phys. Rev. A. 2012. Vol. 86. P. 043415}
\item \foreignlanguage{english}{Jaksch D., Cirac J. I., Zoller P. et al. Fast Quantum Gates for Neutral Atoms//Phys.
Rev. Lett. 2000. Vol. 85. P. 2208--2211.}
\item \foreignlanguage{english}{Yildirim Erol. Accurate determination of the potential energy surface of the potential
energy surfaces and the molecular properties for MHe+ (M=Li, Na, K) complexes using quantum mechanical techniques
[}Текст\foreignlanguage{english}{]: M.Sc Thesis (509031227) / Yildirim Erol; \.Istanbul
Technical University. -- \.Istanbul, 2005. -- 86 }с\foreignlanguage{english}{.}
\item Чернов В. Е.
Высоковозбуждённые электронные состояния в малоатомных системах с несферической симметрией : автореф. дис. ... докт.
физ.-мат. наук : 01.04.05 / В. Е.
Чернов
\item Зон Б. А.
Ридберговские состояния в полярных
молекулах // ЖЭТФ.
\end{enumerate}
\foreignlanguage{english}{1992. \textcyrillic{Т. 102. С. 36.}}

\liststyleWWNumi
\setcounter{saveenum}{\value{enumi}}
\begin{enumerate}
\setcounter{enumi}{\value{saveenum}}
\item Бейтман Г., Эрдейн
А., Высшие трансцендентные
функции [Текст] /
Бейтман Г., Эрдейн
А. \ \ {}-- Москва: Наука, 1973. -- 297
с.
\item \foreignlanguage{english}{\ Gary Simons, New procedure for generating valence and Rydberg orbitals. Atomic
oscillator strengths // J. Chem. Phys. 1974. 60, 645. C.645-649 ;}
\item \foreignlanguage{english}{Martin, A.C. Lavin, M. Velasco, M.O. Martin, J. Karwowski, G.H.F. Diercksen, Quantum
defect orbital study of electronic transitions in Rydbergmolecules: ammonium and fluoronium radicals \ //Chemical
Physics 202 (1996) C. 307-320}
\item \foreignlanguage{english}{\ P. G. Alcheev, V. E. Chernov, and B. A. Zon Oscillator Strengths for Rydberg States in
the Polar Molecule NeH // Journal of Molecular Spectroscopy 211, C. 71--81 (2002)}
\item \foreignlanguage{english}{\ D. Bates and G. Damgaard, The Calculation of the Absolute Strengths of Spectral Lines
// Philos. Trans. R. Soc. A 242, 101--122 (1949)}
\item \foreignlanguage{english}{\ Seaton M. J. The quantum defect theory //1958 Mon. Not. R. Astron. Soc. 118.~C.
504-518}
\item \foreignlanguage{english}{\ P.G. Alcheev, R.J. Buenker, V.E. Chernov, and B.A. Zon, Oscillator strengths for
Rydberg states in ArH calculated in QDT approximation // Journal of Molecular Spectroscopy \ 218 (2003) C. 190--196}
\item \foreignlanguage{english}{\ M. Seaton, Quantum defect theory // Rep. Prog. Phys. 46, C.167--257 (1983)}
\item \foreignlanguage{english}{\ I. Martin, E. Charro \& C. Lavin (2002) Study of Rydberg transitions in NaHe,
Molecular Physics: An International Journal at the Interface Between Chemistry and Physics, 100:4, 465-473}
\item \foreignlanguage{english}{M. Arif, Ch. Jungen, and A. L. Roche. The Rydberg spectrum of CaF and BaF: Calculation
by R-matrix and generalized quantum defect theory / M. Arif, Ch. Jungen, and A. L. Roche \ // The Journal of Chemical
Physics. -- 1997. - 106, 4102. -- }С\foreignlanguage{english}{. 4102 - 4118.}
\item \foreignlanguage{english}{\ Theodorakopoulus G. and Petsalakis,. D,// 1993,J. Phys. B: At. Molec. op/.Phys.. 26,
4367.}
\item \foreignlanguage{english}{\ S. Raynor and D. R. Herschbach, //J. Phys. Chem. 86, 3592--3598 (1982).}
\end{enumerate}

